Embedded Meta-Learning: Toward more flexible deep-learning models

### 2019-05-09 writing/embedded_meta_learning.tex
Typing this hyperparameter table sucked

>>>>

\subsection{Model}

\begin{table}[H]
\centering
\begin{tabular}{|c|ccc|}
\hline 
& \phantom{bla}Polynomials\phantom{la} & Continual learning & \phantom{blahb}Cards\phantom{blahb} \\
\hline
$Z$-dimension & 512 & 512 & 512 \\
$\mathcal{I}$ num. layers & \multicolumn{3}{c|}{3} \\ 
$\mathcal{I}$ num. hidden units & \multicolumn{3}{c|}{64} \\ 
$\mathcal{O}$ num. layers & 1 & 1 & 3 \\ 
$\mathcal{O}$ num. hidden units & - & - & 512 \\ 
$\mathcal{T}$ num. layers & \multicolumn{3}{c|}{1} \\ 
$\mathcal{M}$ architecture & \multicolumn{3}{c|}{2 layers per-datum, max pool across, 2 layers} \\ 
$\mathcal{H}$ architecture & \multicolumn{3}{c|}{4 layers} \\ 
$\mathcal{M}, \mathcal{H}$ num. hidden units & \multicolumn{3}{c|}{512} \\ 
$f$ architecture & \multicolumn{3}{c|}{4 layers} \\ 
$f$ num. hidden units & \multicolumn{3}{c|}{64} \\ 
Nonlinearities & \multicolumn{3}{c|}{Leaky ReLU, no non-linearity at final layer of $T$, $M$, $f$.} \\
\hline
Optimizer & Adam & RMSProp & RMSProp \\
Learning rate (base) & $3\cdot 10^{-5}$ & $1\cdot 10^{-4}$ & $1\cdot 10^{-4}$\\
Learning rate (meta) & $1\cdot 10^{-5}$ & - & $1\cdot 10^{-4}$\\
L.R. decay rate (base) & $*0.85$ & $*0.85$ & $*0.85$ \\
L.R. decay rate (meta) & $*0.85$ & - & $*0.9$ \\
L.R. min (base) & \multicolumn{3}{c|}{$3 \cdot 10^{-8}$} \\
L.R. min (meta) & $1 \cdot 10^{-7}$& - & $3 \cdot 10^{-7}$ \\
L.R. decays every & \multicolumn{3}{c|}{$100$ epochs if above min.} \\
Cached embedding L.R. & - & $1\cdot 10^{-3}$ & -\\
Num. training epochs & 4000 & 3000 & 40000 \\
\hline
Num. base tasks (eval) & 60 & 100 & 36 or 20 \\
Num. base tasks (training) & 1200 (= 60 * 20) & 100 & 36 or 20  \\
Num. meta classifications & 6 & - & 8  \\
Num. meta mappings & 20 & - & 3  \\
Num. new base tasks & 40 & 30 & 4 or 20 \\ 
Num. new meta mappings & 16 & - & 0  \\
Num. new meta classifications &  \multicolumn{3}{c|}{0} \\
Base dataset size & \multicolumn{3}{c|}{1024} \\
Base datasets refreshed & \multicolumn{3}{c|}{Every 50 epochs} \\
$\mathcal{M}$ batch size & 50 & 128 & 768 \\
\hline
\end{tabular}
\caption{Detailed hyperparameter specification for different experiments. A ``-'' indicates a parameter that does not apply to that experiment. Where only one value is given, it applied to all the experiments discussed. Hyperparameters were generally found by a heuristic search. (Some of these parameters take the values they do for fairly arbitrary reasons, e.g. the continual learning experiments were run before the hyperparameter search for the polynomial data was complete, so some parameters are altered between these.)} \label{supp_hyperparameter_table}
\end{table}

As a reminder: the shared representational space is denoted by $Z$. Input encoder: $\mathcal{I}: \text{input} \rightarrow Z$. Output decoder $\mathcal{O}: Z \rightarrow \text{output}$. Target encoder $\mathcal{T}: \text{targets} \rightarrow Z$. Meta-network $\mathcal{M}: \{(Z, Z), ...\} \rightarrow Z $ -- takes a set of (input embedding, target embedding) pairs and produces a function embedding. Hyper-network $\mathcal{h}: Z \rightarrow \text{parameters}$ -- takes a function embedding and produces a set of parameters. Task network $f: Z \rightarrow Z$ -- the transformation that executes the task mapping, implemented by a deep network with parameters specified by $\mathcal{H}$. \par
